Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-05-27 Grassmannian_cells.tex
Section 3 edits

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfJ}{\mathbf{J}}
\newcommand{\bfs}{\mathbf{s}}
\newcommand{\bft}{\mathbf{t}}

@@

The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  Using this, we have the following:
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}

@@

\begin{definition}
  For $V\in \Gr(\cH_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

We collect below several basic homological results related to preprojective representations.
\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in \Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong \cH_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  As $P_m$ is rigid, applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives}, gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
  and an isomorphism
  \[\Ext(P_m,P_{m+1})\cong\Ext(P_m,P_{m+1}^V).\]
  There is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ giving the first claim.
  The second claim follows from the vanishing of $\Ext(P_m,P_{m+1})$ (c.f.~Theorem~\ref{th:rigids}).
\qed\end{proof}

@@

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subseteq V$ and this morphism is unique (up to scalars) when it exists.
    \item For $W\subseteq V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\rightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\rightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero (and hence one-dimensional) if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
  But this occurs exactly when the image of the map $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subseteq V$. 
  In this case, there are isomorphisms
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes \cH_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\qed\end{proof}
\begin{remark}
  The total Grassmannian $\Gr(\cH_m)$ is naturally a poset under inclusion.
  This structure gives rise to a $\CC$-linear category $\CC \Gr(\cH_m)$ with objects the elements of $\Gr(\cH_m)$ and at most one morphism (up to scalars) between any two objects.
  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(\cH_m)$.
  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(\cH_m)\cong\cP_{m+1}$.
\end{remark}

The truncated preprojective representation $P_{m+1}^V$ has dimension vector  $\udim P_{m+1}^V=d(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
For a dimension vector $d=(d_1,d_2)\in\NN^{K(n)_0}$, write 
\[R_d(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
for the affine space of representations of $K(n)$ with dimension vector $d$. 
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The indecomposable representations of $K(n)$ with dimension vector $d(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
    \item The set of indecomposable representations with dimension vector $d(m,r)$ is given by a non-empty open subset of $R_{d(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(d(m,r))^\sigma=d(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $d(m,r)=(l,1)$ for $l:=n-r$.
  This means that $X\in R_{d(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{l\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=l$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=l-k$.

  This shows that the indecomposable representations in $R_{(l,1)}(K(n))$ are in one-to-one correspondence with $l\times n$ matrices of maximal rank.
  Thus we may associate to each such representation $X$ a subspace of $\CC^n$ of dimension~$l$ spanned by the row vectors of the corresponding matrix $M_X$.
  Now it is straightforward to check that the $\GL_{d(m,r)}=\GL_l(\CC)\times\CC^\ast$-action on $R_{d(m,r)}(K(n))$ corresponds to the base change action of $\GL_l(\CC)$ on the set of these subspaces.
  This shows the first statement.

  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives with dimension vector $d(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.

  As there exist representations with trivial endomorphism ring, the dimension vectors $d(m,r)$ are Schur roots.
  It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{d(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the last claim.
\qed\end{proof}
\begin{remark}
  There is a more elegant way to prove the first part of Proposition~\ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(d)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_l(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in\Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
  Recall that $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some indecomposable representation $X$ and some $\ell\ge1$ implies that $X$ is preprojective of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$).
  However, $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
\qed\end{proof}

@@

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows.
\qed\end{proof}
% We proceed by induction on $m$.
% When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
% In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

@@

For $V\in \Gr(\cH_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{corollary}
  \label{cor:base fibers}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$, with $W\subset V$.
  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
\end{corollary}
\begin{proof}
  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives $P_r$ with $1\leq r\leq m$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  must split.
  The claim for arbitrary subrepresentations $Z\subset P_m\otimes(V/W)$ is an immediate consequence of this splitting.
\qed\end{proof}

@@

\begin{lemma}
  \label{le:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $\cH_m^*\cong \cH_{m-1}$.
\end{lemma}
\begin{proof}
  Define a map $\cH_m^*\to \cH_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in \cH_m^*$ is a nonzero functional on $\cH_m$ and let $V\subsetneq \cH_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in \cH_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes \cH_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.
  Thus the map $\cH_m^*\to \cH_{m-1}$, $\varphi\mapsto\bar{\varphi}$ must be injective and hence an isomorphism.
\qed\end{proof}
\begin{remark}
  The set $\Gr(\cH_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $\Gr(\cH_m)^{op}\cong \Gr(\cH_m^*)$ with $\Gr(\cH_{m-1})$.
  We write $\bar{V}\subset \cH_{m-1}$ for the subspace corresponding to $V\subset \cH_m$ under this identification.
  Under the isomorphism of $\cH_m^*$ with $\cH_{m-1}$, we have $\bar{V}=(\cH_m/V)^*$.
\end{remark}

@@

Fix a natural number $n\geq 3$.
Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.
In this section, we fix compatible bases for each $\cH_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.

>>>>

\newcommand{\bfd}{\mathbf{d}}
\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfI}{\mathbf{I}}
\newcommand{\bfJ}{\mathbf{J}}
\newcommand{\bfs}{\mathbf{s}}
\newcommand{\bft}{\mathbf{t}}

@@

The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
The following homological organization is well-known.
\begin{lemma}
  \label{le:preprojective subs}
  If $\Hom(X,P_m)\ne0$ (resp. $\Ext(P_m,X)\ne0$) for some indecomposable representation $X$ and some $m\ge1$, then $X$ must be preprojective of the form $P_r$ with $1\le r\le m$ (resp. $1\le r\le m-2$).
\end{lemma}
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  Using this, we have the following:
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}

@@

\begin{definition}
  For $V\in \Gr(\cH_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$ as this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

We collect below several basic homological results related to truncated preprojective representations.
\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in \Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong \cH_m/V$ and $\Ext(P_m,P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
  As $P_m$ is rigid, applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives}, gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}\]
  and an isomorphism
  \[\Ext(P_m,P_{m+1})\cong\Ext(P_m,P_{m+1}^V).\]
  There is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ giving the first claim.
  The second claim follows from the vanishing of $\Ext(P_m,P_{m+1})$ (c.f.~Theorem~\ref{th:rigids}).
\qed\end{proof}

@@

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subseteq V$, and this morphism is unique (up to scalars) when it exists.
    \item For $W\subseteq V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
      Otherwise, $\Ext(P_{m+1}^W,P_{m+1}^V)$ is naturally isomorphic to the quotient of $W^*\otimes (\cH_m/V)$ by the line corresponding to the standard counit $\CC\to W^*\otimes W$, this line degenerates to a point in the case $W\subseteq V$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\rightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\rightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, therefore $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero (hence one-dimensional) if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
  A routine chase using the following pullback diagram confirms the latter holds if and only if $W\subseteq V$.
  \[\xymatrix{
      & 0 \ar[d] & 0 \ar[d] & 0 \ar[d] \\
      0 \ar[r] & K \ar[r] \ar[d] \ar@{}[dr]|(.7){\lrcorner} & P_m\otimes W \ar[d]^{ev_W} \ar[r] & C \ar[r] \ar[d] & 0\\
    0 \ar[r] & P_m\otimes V \ar[r]^{ev_V} & P_{m+1} \ar[r]^{\pi_V} & P_{m+1}^V \ar[r] & 0}\]

  In case $W\subseteq V$, there are isomorphisms
  \[\Ext(P_{m+1}^W,P_{m+1}^V)\cong\Hom(P_m\otimes W,P_{m+1}^V)\cong W^*\otimes \cH_m/V,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
  Otherwise, we must quotient $\Hom(P_m\otimes W,P_{m+1}^V)$ by the image of $-\circ ev_W$.
  This line can be described as above since that gives $ev_W$ under the isomorphism $W^*\otimes\cH_m\cong\Hom(P_m\otimes W,P_{m+1})$.
\qed\end{proof}
\begin{remark}
  The total Grassmannian $\Gr(\cH_m)$ is naturally a poset under inclusion.
  This structure gives rise to a $\CC$-linear category $\CC \Gr(\cH_m)$ with objects the elements of $\Gr(\cH_m)$ and at most one morphism (up to scalars) between any two objects.
  Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in \Gr(\cH_m)$.
  By Lemma~\ref{le:unique morphisms}(1), the functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC \Gr(\cH_m)\cong\cP_{m+1}$.
\end{remark}

The truncated preprojective representation $P_{m+1}^V$ has dimension vector  $\udim P_{m+1}^V=\bfd(m,\dim V):=\udim P_{m+1}-\dim V\cdot\udim P_m$.
These will play an important role when describing quiver Grassmannians of preprojective representations recursively.
For a dimension vector $\bfd=(d_1,d_2)\in\NN^{K(n)_0}$, write 
\[R_\bfd(K(n))=\bigoplus_{i=1}^n\Hom_{\CC}(\CC^{d_2},\CC^{d_1})\]
for the affine space of representations of $K(n)$ with dimension vector $\bfd$. 
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$ and $0\le r\le n-1$.
  The following hold:
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are in one-to-one correspondence with points of $\Gr_{n-r}(\CC^n)$.
    \item The indecomposable representations of $K(n)$ with dimension vector $\bfd(m,r)$ are precisely the truncated preprojective representations $P_{m+1}^V$ for $V\in \Gr(\cH_m)$ with $\dim V=r$. 
    \item The set of indecomposable representations with dimension vector $\bfd(m,r)$ is given by a non-empty open subset of $R_{\bfd(m,r)}(K(n))$. 
  \end{enumerate}
\end{proposition}
\begin{proof}
  As the reflection functors $\Sigma_1,\,\Sigma_2$ preserve indecomposability and $\Sigma_2(\bfd(m,r))^\sigma=\bfd(m+1,r)$, it suffices to prove the first statement for $m=1$.
  Then we have $\bfd(m,r)=(\ell,1)$ for $\ell:=n-r$.
  This means that $X\in R_{\bfd(m,r)}(K(n))$ can be represented by a matrix $M_X\in\CC^{\ell\times n}$, where the $i^{\mathrm{th}}$ column stands for $X_{\alpha_i}$.
  Now $X$ is indecomposable if and only if $\rk(M_X)=\ell$.
  Indeed, $X$ admits a summand isomorphic to $S_1^k$ exactly when $\rk(M_X)=\ell-k$.

  This shows that the indecomposable representations in $R_{(\ell,1)}(K(n))$ are in one-to-one correspondence with $\ell\times n$ matrices of maximal rank.
  Thus we may associate to each such representation $X$ a subspace of $\CC^n$ of dimension~$\ell$ spanned by the row vectors of the corresponding matrix $M_X$.
  Now it is straightforward to check that the $\GL_{\bfd(m,r)}=\GL_\ell(\CC)\times\CC^\ast$-action on $R_{\bfd(m,r)}(K(n))$ corresponds to the base change action of $\GL_\ell(\CC)$ on the set of these subspaces.
  This shows the first statement.

  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
  Since both the isomorphism classes of indecomposables and the isomorphism classes of truncated projectives with dimension vector $\bfd(m,r)$ are parametrized by the same Grassmannian, this gives the second claim.

  As there exist representations with trivial endomorphism ring, the dimension vectors $\bfd(m,r)$ are Schur roots.
  It follows that the set of indecomposable representations with trivial endomorphism ring forms a dense open subset of $R_{\bfd(m,r)}(K(n))$, see for example \cite[Theorem 2.2]{sch}.
  This shows the last claim.
\qed\end{proof}
\begin{remark}
  There is a more elegant way to prove the first part of Proposition~\ref{pro:indecomposables} using the notion of stability and moduli spaces.
  Actually, fixing the standard stability induced by the linear form $\Theta:\ZZ^{Q_0}\to\ZZ$ defined by $\Theta(\bfd)=d_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representations is in fact $\Gr_\ell(\CC^n)$.
  We opted for the proof above because the notion of stability would only be used at this point and we wanted to keep the exposition as simple as possible. 
\end{remark}

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in\Gr(\cH_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
\end{lemma}
\begin{proof}
   The representation $P_{m+1}^V$ is indecomposable by Proposition~\ref{pro:indecomposables} and it cannot be preprojective as it is not rigid by Lemma~\ref{le:unique morphisms}.
   The claim then follows from Lemma~\ref{le:preprojective subs}.
\qed\end{proof}

@@

\begin{lemma}
  \label{le:projective subrepresentations}
  For $V\in \Gr(\cH_m)$, $m\ge1$, any proper subrepresentation $X\subsetneq P_{m+1}^V$ can be written as a direct sum of preprojective representations $P_r$ with $1\le r\le m$.
\end{lemma}
\begin{proof}
  Since the map $ev_V$ in equation \eqref{eq:truncated preprojectives} is irreducible, every proper subrepresentation of $P_{m+1}^V$ factors through $P_{m+1}$ and the claim follows from Lemma~\ref{le:preprojective subs}.
\qed\end{proof}
% We proceed by induction on $m$.
% When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
% In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

@@

For $V\in \Gr(\cH_m)$, $m\ge1$, any subspace $W\subset V$ gives rise to an exact sequence
\[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar[r]^(.6){ev} & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0},\]
where the left hand morphism above is the natural evaluation morphism coming from Lemma~\ref{le:truncated homomorphisms}.
Each such sequence has the following almost-split property for proper subrepresentations of $P_{m+1}^V$.
\begin{corollary}
  \label{cor:base fibers}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$, with $W\subset V$.
  Given any proper subrepresentation $X\subsetneq P_{m+1}^V$ and any subrepresentation $Z\subset P_m\otimes(V/W)$, there is a subrepresentation of $P_{m+1}^W$ isomorphic to $Z\oplus X$ which fits into a commutative diagram
  \[\xymatrix{0 \ar[r] & Z \ar[d]\ar[r] & Z\oplus X \ar[r]\ar[d] & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
\end{corollary}
\begin{proof}
  Observe that $\Ext(P_r,P_m)=0$ for $1\le r\le m$ and, since $X$ is a direct sum of preprojectives $P_r$ with $1\leq r\leq m$, the upper pullback sequence
  \[\xymatrix{0 \ar[r] & P_m\otimes(V/W) \ar@{=}[d]\ar[r] & Y \ar[r]\ar[d]\ar@{}[dr]|(.7){\lrcorner} & X \ar[d]\ar[r] & 0 \\
    0 \ar[r] & P_m\otimes(V/W) \ar[r] & P_{m+1}^W \ar[r] & P_{m+1}^V \ar[r] & 0}\]
  must split.
  The claim for an arbitrary subrepresentation $Z\subseteq P_m\otimes(V/W)$ is an immediate consequence of this splitting.
\qed\end{proof}

@@

\begin{lemma}
  \label{le:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $\cH_m^*\cong \cH_{m-1}$.
\end{lemma}
\begin{proof}
  Define a map $\cH_m^*\to \cH_{m-1}$ by $\varphi\mapsto\bar{\varphi}:=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\bar{\varphi}$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in \cH_m^*$ is a nonzero functional on $\cH_m$ and let $V\subsetneq \cH_m$ denote the kernel of $\varphi$.
  Then $\bar{\varphi}=0\in \cH_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes \cH_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $ev\circ\iota_{m-1}=ev_V\circ\iota_{m-1}\ne0$, a contradiction.
  Thus the map $\cH_m^*\to \cH_{m-1}$, $\varphi\mapsto\bar{\varphi}$, must be injective and hence an isomorphism.
\qed\end{proof}
\begin{remark}
  The set $\Gr(\cH_m)$ is naturally a poset and Lemma~\ref{le:preprojective homomorphism duality} gives an identification of the opposite poset $\Gr(\cH_m)^{op}\cong \Gr(\cH_m^*)$ with $\Gr(\cH_{m-1})$.
  We write $\bar{V}\subset \cH_{m-1}$ for the subspace corresponding to $V\subset \cH_m$ under this identification.
  Under the isomorphism of $\cH_m^*$ with $\cH_{m-1}$, we have $\bar{V}=(\cH_m/V)^*$.
\end{remark}

@@

Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.
In this section, we fix compatible bases for each $\cH_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.
